Evolution of the AGN UV luminosity function from redshift 7.5

### 2019-02-21 Paper/paper.tex
Update

\documentclass[fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}
\def\lya{Ly$\alpha$~}
\def\HI{\hbox{H~$\scriptstyle\rm I$}}
\def\HII{\hbox{H~$\scriptstyle\rm II$}}
\def\nHI{{\rm HI}}
\def\nH{{\rm H}}
\def\nHII{{\rm HII}}
\def\nHe{{\rm He}}
\def\nHeI{{\rm HeI}}
\def\nHeII{{\rm HeII}}
\def\nHeIII{{\rm HeIII}}
\def\bHII{\hbox{\bf H~$\scriptstyle\bf II$}}
\def\HeI{\hbox{He~$\scriptstyle\rm I$}}
\def\HeII{\hbox{He~$\scriptstyle\rm II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\def\bHeII{\hbox{\bf He~$\scriptstyle\bf II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\usepackage{dcolumn}
\newcolumntype{.}{D{.}{.}{2.7}}
\newcolumntype{e}{D{.}{.}{2.10}}
\newcolumntype{d}{D{.}{.}{2.3}}

@@

At $2.2<z<3.5$ we used a single sample of 23,301 uniformly
colour-selected quasars from 2236\,deg$^2$ in BOSS DR9
\citep{2013ApJ...773...14R} due to several improvements compared to
previous surveys. First, it covers a similar magnitude range as 2SLAQ
but with $>20$ times as many quasars. Second, although the SDSS DR7
sample provides better coverage of the bright end of the QLF at these
redshifts, its selection function is highly dependent on the assumed
incidence of (partial) Lyman limit systems in the IGM
\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. While the BOSS DR9
selection function considers these improvements, the uncertainty in
the QLF remains dominated by assumptions in the selection function
given the large sample size
\citep{2013ApJ...773...14R}. Variability-selected quasar samples
circumvent this issue \citep{2013ApJ...773...14R, 2013A&A...551A..29P,
  2016A&A...587A..41P}, but may be affected by (i) single-epoch
imaging incompleteness at the faint end \citep{2013ApJ...773...14R},
and (ii) uncertainties in the selection function caused by the limited
number of known $z\ga 3$ quasars not selected by variability in the
same footprint \citep{2013A&A...551A..29P, 2016A&A...587A..41P}.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
    % mosaic_selected.py and drawlf_selected.py 
  \end{center}
  \caption{Luminosity function estimates from $z=0.6$ to $6.5$.
    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
    binned luminosity functions.  In each redshift bin, yellow curves
    show our fiducial double power law luminosity function model in
    that redshift bin.  Other curves show the three global evolution
    models.  Shaded regions show the one-sigma (68.26\%)
    uncertainties.}
  \label{fig:mosaic_global}
\end{figure*}

@@

Figure~\ref{fig:mosaic_global} shows the three global models in
comparison with the binned fits from the previous section.  The shaded
regions show the one-sigma (68.26\%) uncertainty.  The symbols show
the luminosity function binned in luminosity and redshift, and the
yellow shaded regions show the posterior distribution of the double
power law luminosity functions in various redshift bins, as in
Figure~\ref{fig:mosaic}.  Bins containing data with large systematic
error are excluded from Figure~\ref{fig:mosaic_global}.  All three
global models are in excellent agreement with the binned models,
although Model~1 performs better.

@@

\begin{figure*}
  \begin{center}
    % rtg2.draw_g_paper() 
    \includegraphics[scale=0.65]{g.pdf}
  \end{center}
  \caption{AGN contribution to the hydrogen photoionization rate, when
    the AGN luminosity function is integrated down to $M_{1450}=-21$
    (blue curve and shaded region) and $M_{1450}=-18$ (red curve and
    shaded region).  The shaded regions show the one-sigma (68.26\%)
    uncertainty.  Also shown are the photoionization rate measurements
    by \citet[filled circles]{2013MNRAS.436.1023B}, \citet[inverted
      triangles]{2011MNRAS.412.2543C},
    \citet[triangles]{2011MNRAS.412.1926W}, \citet[blue
      hexagons]{2018MNRAS.473..560D} and \citet[green
      squares]{2018ApJ...855..106D}, and
    \citet[pentagons]{2017MNRAS.467.3172G}, and models of
    \citet[dotted brown curve]{2012ApJ...746..125H}, the QSO
    contribution in this model (dashed grey), \citet[dashed
      brown]{2015ApJ...813L...8M}, the QSO contribution from the model
    of \citet[dashed orange]{2015MNRAS.451L..30K}, \citet[dotted
      grey]{2017ApJ...837..106O}, and \citet[dashed
      grey]{2018arXiv180104931P}.  The photoionization rate derived
    from the luminosity function fits of \citet{2015AA...578A..83G}
    are shown by the red open circles.}
  \label{fig:gammapi}
\end{figure*}

@@

Using the homogenised data and code that we make publicly available
(Appendix \ref{sec:code}), the luminosity functions presented in this
paper can be easily compared with theoretical models or future data
sets.  These luminosity function determinations supersede previous
determinations by \citet{2007ApJ...654..731H} by including new data,
by analysing unbinned data, and extending the analysis to higher
redshifts.  Our public code can be used either to reproduce all of our
analysis starting from the QSO catalogues, or to quickly evaluate our
luminosity function fits at desired redshifts and luminosities.

@@

\begin{figure*}
  \begin{center}
    % summary_grand.py
    \includegraphics[width=0.7\textwidth]{evolution_grand.pdf}
  \end{center}
  \caption{A comparison of our inferred double power law parameter
    values with those reported in the literature.  Black points show
    our determinations from Figure~\ref{fig:evoln}.  Blue points show
    other values, from \citet[triangles]{2012ApJ...755..169M},
    \citet[squares]{2016ApJ...833..222J},
    \citet[diamonds]{2011ApJ...728L..26G},
    \citet[crosses]{2013ApJ...768..105M}, \citet[downward
      triangles]{2015AA...578A..83G},
    \citet[pentagons]{2018PASJ...70S..34A}, \citet[leftward
      triangles]{2017ApJ...847L..15O},
    \citet[asterisks]{2016ApJ...829...33Y},
    \citet[circles]{2013ApJ...773...14R}, and \citet[rightward
      triangles]{2009A&A...507..781S}.  Where necessary, values from
    the literature have been converted to our cosmology.
    \label{fig:params_grand}}
\end{figure*}

>>>>

\documentclass[fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{xcolor}
\definecolor{notecolor}{rgb}{0.8,0,0}
\newcommand{\new}[1]{{\color{notecolor} #1}}
\usepackage{pdflscape}
\usepackage{siunitx}
\def\lya{Ly$\alpha$~}
\def\HI{\hbox{H~$\scriptstyle\rm I$}}
\def\HII{\hbox{H~$\scriptstyle\rm II$}}
\def\nHI{{\rm HI}}
\def\nH{{\rm H}}
\def\nHII{{\rm HII}}
\def\nHe{{\rm He}}
\def\nHeI{{\rm HeI}}
\def\nHeII{{\rm HeII}}
\def\nHeIII{{\rm HeIII}}
\def\bHII{\hbox{\bf H~$\scriptstyle\bf II$}}
\def\HeI{\hbox{He~$\scriptstyle\rm I$}}
\def\HeII{\hbox{He~$\scriptstyle\rm II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\def\bHeII{\hbox{\bf He~$\scriptstyle\bf II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\usepackage{dcolumn}
\newcolumntype{.}{D{.}{.}{2.7}}
\newcolumntype{e}{D{.}{.}{2.10}}
\newcolumntype{d}{D{.}{.}{2.3}}

@@

At $2.2<z<3.5$ we used a single sample of 23,301 uniformly
colour-selected quasars from 2236\,deg$^2$ in BOSS DR9
\citep{2013ApJ...773...14R} due to several improvements compared to
previous surveys. First, it covers a similar magnitude range as 2SLAQ
but with $>20$ times as many quasars. Second, although the SDSS DR7
sample provides better coverage of the bright end of the QLF at these
redshifts, its selection function is highly dependent on the assumed
incidence of (partial) Lyman limit systems in the IGM
\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}.  \new{The BOSS DR9
selection function incorporates an improved treatment of the QSO SED
and the IGM, including stochasticity in the colour distribution due to
intervening Lyman-limit systems.}  While the BOSS DR9 selection
function considers these improvements, the uncertainty in the QLF
remains dominated by assumptions in the selection function given the
large sample size \citep{2013ApJ...773...14R}.  Variability-selected
quasar samples circumvent this issue \citep{2013ApJ...773...14R,
  2013A&A...551A..29P, 2016A&A...587A..41P}, but may be affected by
(i) single-epoch imaging incompleteness at the faint end
\citep{2013ApJ...773...14R}, and (ii) uncertainties in the selection
function caused by the limited number of known $z\ga 3$ quasars not
selected by variability in the same footprint
\citep{2013A&A...551A..29P, 2016A&A...587A..41P}.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
    % mosaic_selected.py
  \end{center}
  \caption{Luminosity function estimates from $z=0.6$ to $6.5$.
    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
    binned luminosity functions.  In each redshift bin, yellow curves
    show our fiducial double power law luminosity function model in
    that redshift bin.  Other curves show the three global evolution
    models.  Shaded regions show the one-sigma (68.26\%)
    uncertainties.}
  \label{fig:mosaic_global}
\end{figure*}

@@

Figure~\ref{fig:mosaic_global} shows the three global models in
comparison with the binned fits from the previous section.  The shaded
regions show the one-sigma (68.26\%) uncertainty.  The symbols show
the luminosity function binned in luminosity and redshift, and the
yellow shaded regions show the posterior distribution of the double
power law luminosity functions in various redshift bins, as in
Figure~\ref{fig:mosaic}.  Bins containing data with large systematic
error are excluded from Figure~\ref{fig:mosaic_global}.  \new{All
  three global models are in good agreement with the luminosity
  functions in redshift bins, although Model~1 reproduces best the
  apparent rapid evolution in the faint-end slope $\beta$ at $z>4$.
  Given the systematic errors in the data, a quantitative model
  selection is of limited use.}

@@

\begin{figure*}
  \begin{center}
    % rtg2.draw_g_paper() 
    \includegraphics[scale=0.65]{g.pdf}
  \end{center}
  \caption{AGN contribution to the hydrogen photoionization rate, when
    the AGN luminosity function is integrated down to $M_{1450}=-21$
    (blue curve and shaded region) and $M_{1450}=-18$ (red curve and
    shaded region).  The shaded regions show the one-sigma (68.26\%)
    uncertainty.  Also shown are the photoionization rate measurements
    by \citet[filled circles]{2013MNRAS.436.1023B}, \citet[inverted
      triangles]{2011MNRAS.412.2543C},
    \citet[triangles]{2011MNRAS.412.1926W}, \citet[blue
      hexagons]{2018MNRAS.473..560D} and \citet[green
      squares]{2018ApJ...855..106D}, and
    \citet[pentagons]{2017MNRAS.467.3172G}, and models of
    \citet[dotted brown curve]{2012ApJ...746..125H}, the QSO
    contribution in this model (\new{dashed brown}),
    \citet[\new{dotted green}]{2015ApJ...813L...8M}, the QSO
    contribution from the model of \citet[dashed
      orange]{2015MNRAS.451L..30K}, \citet[dotted
      grey]{2017ApJ...837..106O}, and \citet[dashed
      grey]{2018arXiv180104931P}.  The photoionization rate derived
    from the luminosity function fits of \citet{2015AA...578A..83G}
    are shown by the red open circles.}
  \label{fig:gammapi}
\end{figure*}

@@

Using the homogenised data and code that we make publicly available
(Appendix \ref{sec:code}), the luminosity functions presented in this
paper can be easily compared with theoretical models or future data
sets.  \new{These luminosity functions update previous determinations
  by including new data, by analysing unbinned data, and extending the
  analysis to higher redshifts.}  Our public code can be used either
to reproduce all of our analysis starting from the QSO catalogues, or
to quickly evaluate our luminosity function fits at desired redshifts
and luminosities.

@@

\begin{figure*}
  \begin{center}
    % summary_grand.py
    \includegraphics[width=0.7\textwidth]{evolution_grand.pdf}
  \end{center}
  \caption{A comparison of our inferred double power law parameter
    values with those reported in the literature.  Black points show
    our determinations from Figure~\ref{fig:evoln}.  Blue points show
    other values, from \citet[triangles]{2012ApJ...755..169M},
    \citet[squares]{2016ApJ...833..222J},
    \citet[diamonds]{2011ApJ...728L..26G},
    \citet[crosses]{2013ApJ...768..105M}, \citet[downward
      triangles]{2015AA...578A..83G},
    \citet[pentagons]{2018PASJ...70S..34A}, \citet[leftward
      triangles]{2017ApJ...847L..15O},
    \citet[asterisks]{2016ApJ...829...33Y},
    \citet[circles]{2013ApJ...773...14R},
    \new{\citet[hexagons]{2009MNRAS.399.1755C}} and \citet[rightward
      triangles]{2009A&A...507..781S}.  Where necessary, values from
    the literature have been converted to our cosmology.
    \label{fig:params_grand}}
\end{figure*}
